### 2017-02-28 2017mergingmerges/section/02-Processes.tex
S2 wibble prose

A \emph{process} in our system is a simple imperative program with a local heap. A process pulls source from an arbitrary number of input streams and pushes result values to at least one output stream. The process language is an intermediate representation we use when fusing the overall dataflow network. When describing the fusion transform we describe the control flow of the process as a state machine, hence Machine Fusion.

@@

The definition of the @group@ combinator which detects groups of successive identical elements in input stream is given in Fig.~\ref{fig:Process:Group}. The process emits the first value pulled from the stream and every value that is different from the last one that was pulled. For example, when executed on the input stream @[1,2,2,3]@, the process will produce the output @[1,2,3]@. We include the concrete representation and a diagram of the process viewed as a state machine.

>>>>

A \emph{process} in our system is a simple imperative program with a local heap. A process pulls source values from an arbitrary number of input streams and pushes result values to at least one output stream. The process language is an intermediate representation we use when fusing the overall dataflow network. When describing the fusion transform we describe the control flow of the process as a state machine, hence Machine Fusion.

@@

The definition of the @group@ combinator which detects groups of successive identical elements in the input stream is given in Fig.~\ref{fig:Process:Group}. The process emits the first value pulled from the stream and every value that is different from the last one that was pulled. For example, when executed on the input stream @[1,2,2,3]@, the process will produce the output @[1,2,3]@. We include the concrete representation and a diagram of the process viewed as a state machine.
